High fidelity optimization using gradient based approaches have become more and
more popular. This may be explained through the fact that they do not suffer
from the \textit{curse of dimensionality}. This allows them to have a much
higher number of design variables (dvs) compared to alternatives such as genetic
optimization approaches. The drawback is, of course, one must compute the
gradients in an efficient manner. The \textit{MACH-Aero} Framework offers a set
of tools for gradient based high-fidelity optimization. Part of this Framework
is a CFD solver called \textit{ADflow} which has only one working turbulence
model. This project aims to change that through the implementation of the $k$ -
$\omega$ \textit{Shear Stress Transport (SST)} model.








\section{ADflow}
ADflow is an open-source multi-block\footnote{Overset meshes are also
possible.} Computational Fluid Dynamics (CFD) solver. It solves the Reynolds
Averaged Navier Stokes (RANS) equations to obtain the flow solution. It is
developed and maintained at the \textit{MDOLab} at the university of Michigan
and was based on a CFD solver for turbo machinery called \textit{sumb}. It has
later been adopted  for gradient based optimization by means of
\textit{Algorithmic Differentiation}\footnote{Thats what AD stands for in
ADflow.} and the \textit{adjoint method}. Most of ADflow is written in Fortran.
But it is interfaced in Python. This means, the heavy lifting is done in a fast
language, but the regular user has the benefits of an object-oriented high
level interpreter language.
 
In optimization, a lot of simulations are necessary until an optimal design is
found. It is also highly important to always get an objective value for each
design, even if, or especially when, it is unphysical. Otherwise the optimizer
does not know how bad the current design is. To cater those concerns, ADflow
employs some highly efficient and robust NK\footnote{NK stands for the
Newton–Krylov method.} and ANK\footnote{ANK is an approximated Newton–Krylov
method.} solvers. Those can achieve machine-precision convergence, even for
aircraft configurations at an angle of attack of 90\degree \cite{Mader2020a}
\cite{Kenway2019a} \cite{Yildirim2019b}.

When the solver was still called sumb, various turbulence models such as
Spalart-Allmaras, Spalart-Allmaras with Edwards Modification, $k$ - $\omega$
Wilox, $k$ - $\omega$ Wilox modified, $k$ - $\tau$, v2-f and Menter SST were
implemented. The subsequent modification for optimizations changed the
structure dramatically and only the SA model was carried over. But this means,
a skeleton implementation of SST is available and only the structural changes
need to be incorporated.


\section{Goals}
As stated above, the legacy code for SST is still available but does not really
work anymore. The goal for this project is to get it working for simulation and
optimization. The necessary sub-steps may be summarized as follows. Please note
some in-depth knowledge is needed to understand them. But this will be
explained in later sections of this report:

\begin{enumerate}
    \item Get the current SST model running using a legacy DADI-method.

    \item Modify it in such a way that it is automatically differentiate-able.

    \item Actually differentiate it through \textit{Automatic/Algorithmic
        Differentiation (AD)}.

    \item Make sure the partial AD derivatives are correct. 

    \item Get the NK/ANK Solver working.

    \item Test and verify the implementation

    \item Get the adjoint Solver working.

    \item Test and verify the total gradients.
\end{enumerate}








\section{Code contributions}
Part of this project is a code contribution to ADflow and a setup of test
cases, both can be found on GitHub under those links:\\

\begin{tabular}{l l}
    ADflow Pull Request &
    \url{https://github.com/mdolab/adflow/pull/301}\footnotemark \\

    Test cases & \url{https://github.com/DavidAnderegg/SST_rough_testcases}
\end{tabular}


\footnotetext{The commit at the time of writing was: \texttt{361bf3e9a2e1e4fee177becfdc94f1e48809fa2e}}
